\documentclass[11pt]{article}

%\usepackage[english]{babel}
\usepackage{titlesec}
\usepackage{hyperref}
\hypersetup{ colorlinks=true }

\usepackage{lipsum}
\usepackage{hyphenat}
\usepackage{ragged2e}

\usepackage[a4paper, total={8in, 10in}]{geometry}

\usepackage[defernumbers=true]{biblatex}

\titleformat{\section}[block]{\Large\bfseries\filcenter}{}{1em}{}

\titleformat{\subsection}[block]{\Large\bfseries}{}{}{}[{\titlerule[0.8pt]}]

\titleformat{\subsubsection}[block]{\bfseries}{}{}{}

\author{Vladislav Shubin}

\title{Vladislav Shubin}

\addbibresource{ownbib.bib}

\begin{document}

\section*{Vladislav Shubin}

\begin{center}
	Email: \href{mailto:v.v.choubine@gmail.com}{v.v.choubine@gmail.com}
	
	Personal website: \href{https://supxinfy.github.io}{supxinfy.github.io}
\end{center}

\subsection*{Education}

\textbf{Stockholm University [\href{https://www.su.se}{website}]}, \textit{Sweden}\hfill(2023--present)

I'm getting my master's degree in Mathematics at the Stockholm University.

\subsubsection*{Courses}
\begin{itemize}
\item\textbf{MM7024.} Linear algebra and learning from data.
\item\textbf{MM7029.} Mathematics of cryptography.
\item\textbf{MM8036.} Type theory.
\end{itemize}

\vspace{2mm}
\noindent\textbf{Petrozavodsk State University [\href{https://petrsu.ru}{website}]}, \textit{Russia}\hfill(2019--2023)
\textbf{Bachelor's degree in mathematics}.
\subsubsection*{Courses}
\begin{itemize}
\item\textbf{} \textit{Applicable Statistics}.
\item\textbf{} \textit{Probability theory and Statistics}.
\item\textbf{} \textit{Actuarial Mathematics}.
\item\textbf{} \textit{Financial Mathematics}.
\item\textbf{} \textit{Programming}.
\end{itemize}

I got my bachelor's degree in Mathematics at the Petrozavodsk University.

\vspace{2mm}
\noindent\textbf{School of Computer Science ``Vector++'' [\href{https://www.vector-plus-plus.ru}{website}]}, \textit{Russia}\hfill(2013--2017)

I got a certificate in C/C++ programming and Linux administration skills. Also, I had experience making learning materials and worked with libraries SFML, OpenGL, and OpenCV.

\vspace{2mm}
\noindent\textbf{Summer Project School of Innopolis University [\href{https://team-project.university.innopolis.ru/projectschool2018}{website}]}, \textit{Russia}\hfill(2018) 

I was studying blockchain technology (ETH) at Innopolis University. 

\subsection*{Professional Experience}

\vspace{2mm}
\noindent\textbf{School ``Kventin'' [\href{https://kventinptz.ru}{website}]}, \textit{Russia}\hfill(2020--2023)

I was in a teacher position in computer science and mathematics. Moreover, I've kept computer systems sustainable and reliable.

\vspace{2mm}
\noindent\textbf{Online School ``Start'' [\href{http://schoolprogstart.tilda.ws}{website}]}, \textit{Russia}\hfill(2017--2020)

I was a teacher in online courses on C/C++ programming and Linux administration. 

\vspace{2mm}
\noindent\textbf{Private Tutor/Entrepreneur in Computer Science}, \textit{Russia}\hfill(2017--2023)

I've been a private tutor in computer science and math from 2017 to 2023.

%% If you just want everything in one list
% \printbibliography[heading={none}]

\nocite{*}
\printbibliography[heading={subbibliography},title={Journal Articles},type=article]

\printbibliography[heading={subbibliography},title={Conference Proceedings},type=inproceedings]

% \prinstbibliography[heading={subbibliography},title={Books and Chapters},filter={booksandchapters}]

% \printbibliography

\subsubsection*{OEIS contributions}
I authored the following OEIS sequences:

\noindent\href{https://oeis.org/A355045}{A355045}, \href{https://oeis.org/A355059}{A355059}, \href{https://oeis.org/A337775}{A337775}, \href{https://oeis.org/A337776}{A337776},

\noindent and also contributed to: \href{https://oeis.org/A000108}{A000108}.


% \subsection*{Skills}
% \noindent\textbf{Languages:}
% 	English (fluent), Russian (native), and Swedish (elementary).
%
% \noindent\textbf{Coding:}
% 	 Python, C/C++, Wolfram Mathematics, SageMath, Git, SQL.
%
% \noindent\textbf{Web development:}
% 	\textsc{Html, css}, JavaScript, Typescript, Node.js, Hugo.
%
% \noindent\textbf{Misc:}
% 	Academic research, teaching, \LaTeX\ typesetting and publishing.

\end{document}
